---
title: "Who does more pushups"
author: "Avelyn Potot"
date: "September 22"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```

<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the football team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of running and catching:  they are the quarterback, running backs, receivers, etc.

>We have to identify,classify and analyze our research question and to explain further what tools we use on the data in this question.
OUr research question is:
>Who does more pushups, on average: a line player or a skill player?

# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

>On this method we will both use graphical method and a numerical method to show our the difference of data which is "pushups".Then we will explain the data that we came up along with graphical data and numerical data.We will also use a different branches for each major section.

# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->

>To view the results we have to consider our data base on our source editor down below. This is we where to start our graphical and numerical data.
```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```


## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->
```{r}
xyplot(pushups ~ weight,
	data = pushups,
	groups = position,
	auto.key = list(
		space = "top",
		title = "position",
		cex.title = 1,
		columns = 1),
	main = "who does more more push ups",
	sub = "line player vs. skill player",
	xlab = "weight",
	ylab = "pushups")
```


>I use lattice scatter plot for my graphical method for it easy to identify the difference.
As you can see it has pink dots which represents skill player while blue dots represents line player.The skill player shows more than a hundred pushups,108 to be specific but about 260lbs give or take is the heighest weight. Meanwhile,the line player has 34 heighest pushups but has 300 lbs of weight.Based on the graph, there is more pink dots on the pushups side rather than blue dots on the weight side.This can also be base on the weight and height ratio.The statistics based on this graph is 3:1 ratio.

## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
xtabs (~position+ pushups ,data=pushups)

```

>This numerical result will shows the player who does more pushups according to their position.Every number 1 represent a person who does the push ups base on the position. If you take a closer look  Skill player does more scores up to 108 compared to the line player.

```{r}
xtabs (~weight + position,data=pushups)
```

>In another way to look at the data is to show the weigh difference of each team who took the push ups.The lowest weight of the person who has 152lbs.took the pushups is from the skill players, and the heaviest from this team weigh 260 lbs. However, the Line players has a weigh from 217 lbs. and has a record of heaviest weights took the push ups which is from 272 up to 300.

# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

>I will now run the summary of the data.This showed us the minimum and maximum to show the range of the data.It showed the minimum weight who does push ups is 151 and the minimum push ups made was only 6.The mean of the data is 213 which are the total amount of weight divided by the total amount the weights.We has 5,153/24 we come up of give or take 213.7 and we round it off into 214.Our push ups had a total of 1200/29 which come up of the total of 41.3 whih is correct for our mean data.the Line player had 8 person took the pushups while 22 persons from skill players.

```{r}
summary(pushups)

```


```{r}
t.test(pushups$pushups,pushups$weight)
```

>Our p-value is not equal to 0.Which means that there is a big difference our data.
The mean of our x and y are correct based on the summary of our pushups and weight of our graphical as well as the numerical of our data.

# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

